Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-08-09 geometry.tex
Fix arrow transformation

\documentclass[border=0pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes,
  3d
}
\tikzfading[name=fade img right,left color=transparent!100, right color=transparent!0]
\tikzfading[name=fade img left,right color=transparent!100, left color=transparent!0]
\tikzstyle{snakearrow} = [decorate, decoration={pre length=0.1cm,
  post length=0.1cm, snake, amplitude=.4mm,
  segment length=4mm},thick, ->]
\usepackage{graphicx}
\begin{document}
\newcommand*{\arrowthreeD}[5]{%
  \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
  shift = {#2},
  opacity=0.9,
  rotate=#3,shading=axis,shading angle=90+#3]
  (0,0) -- (80:#4) arc (80:100:#4) -- cycle;
  \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
  shift = {#2},
  opacity=0.9,
  rotate=#3,shading=axis,shading angle=90+#3]
  (87:#4) -- ++(0, #5) -- ++(-{2 * #4 * sin(3)}, 0) -- (93:#4) -- cycle;
}
\begin{tikzpicture}
  \pgfmathsetmacro{\radiush}{1.6}
  \pgfmathsetmacro{\theight}{4}
  \pgfmathsetmacro{\radiusv}{.7 * \radiush}
  \pgfmathsetmacro{\waist}{.15}
  \pgfmathsetmacro{\xscale}{\radiush / sqrt(1 + (\waist)^2)}

@@

  \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.2};
  \path (3.4, 0) node[above,orange!80!black] {Raman F2};
  \path (3, 0) node[below,orange!80!black] {\textbf{R3}};

  \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.8]
  (-1:3.4) arc (-2:-29:3.4 and 1.65);
  \path (-10:3.3) node[orange!50!black, right] {$42^\circ$};

>>>>

\documentclass[border=0pt]{standalone}
\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing,
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes,
  3d
}
\tikzfading[name=fade img right,left color=transparent!100, right color=transparent!0]
\tikzfading[name=fade img left,right color=transparent!100, left color=transparent!0]
\tikzstyle{snakearrow} = [decorate, decoration={pre length=0.1cm,
  post length=0.1cm, snake, amplitude=.4mm,
  segment length=4mm},thick, ->]
\usepackage{graphicx}
\begin{document}
\newcommand*{\arrowthreeD}[5]{%
  \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
  opacity=0.9,
  transform canvas={shift={#2}, rotate=#3},shading=axis,shading angle=90]
  (0,0) -- (80:#4) arc (80:100:#4) -- cycle;
  \fill[left color=#1!50!black,right color=#1!50!black,middle color=#1!43,
  opacity=0.9,
  transform canvas={shift={#2}, rotate=#3},shading=axis,shading angle=90]
  (87:#4) -- ++(0, #5) -- ++(-{2 * #4 * sin(3)}, 0) -- (93:#4) -- cycle;
}
\begin{tikzpicture}
  \pgfmathsetmacro{\radiush}{1.5}
  \pgfmathsetmacro{\theight}{4}
  \pgfmathsetmacro{\radiusv}{.7 * \radiush}
  \pgfmathsetmacro{\waist}{.15}
  \pgfmathsetmacro{\xscale}{\radiush / sqrt(1 + (\waist)^2)}

@@

  \begin{scope}[transform canvas={rotate={4}}]
    \arrowthreeD{orange}{(0.6, 0)}{-90}{0.4}{3.2};
    \path (3.4, 0) node[above,orange!80!black] {Raman F2};
    \path (3, 0) node[below,orange!80!black] {\textbf{R3}};
  \end{scope}

  \draw[orange!50!black, <->, densely dotted, >=stealth, line width=0.8]
  (3:3.4) arc (3:-32:3.4 and 1.65);
  \path (-6:3.3) node[orange!50!black, right] {$42^\circ$};
